Syntactic realization with data-driven neural tree grammars

### 2016-10-11 paper/draft.tex
down to length

By contrast, neural techniques work by embedding such tokens into a
vector space. This process learns an abstract representation of tokens
that clusters similar items together and makes further predictions
as a function of those items' learned features.  The resulting
abilities to generalize across sparse data seems to be one of the most
important reasons for the success of deep learning in NLP.

@@

The nodes of a supertag can be independently embedded and combined to form a
tensor of embeddings.
%
Specifically, symbols representing the syntactic category and node roles are treated as
distinct vocabulary tokens, mapped to integers, and used to retrieve a vector
representation that is learned during training.
%
The vectors are grouped into a tensor by placing the root node into the
first cell of the first row and left-aligning the descendants in the subsequent rows.
%
The two tensors are combined by concatenating along the embedding dimension.
%
This embed-and-group method is shown in on the left in Figure \ref{fig:spineembedding}.
%the root node is in first cell in the first row and the subsequent nodes are

@@

The use of topological indices allows for many recurrent tree networks to be
run in parallel on a GPU, increasing the efficiency of the implementation.
%
The primary concern for running parallel GPU computations is homogeneity because
the same operation will be applied to the entire data structure.
%
Normally, tree operations require flow control, making homogeneity impossible.
%
However, using topological indices and a tree state eliminates the need for flow control
by creating locally linear, homogeneous computations.

>>>>

By contrast, neural techniques work by embedding such tokens into a
vector space. This process learns an abstract representation of tokens
that clusters similar items together and makes further predictions
as a function of those items' learned features.  The resulting
ability to generalize across sparse data seems to be one of the most
important reasons for the success of deep learning in NLP.

@@

We first embed each node independently, then combined the vectors to
form a tensor of embeddings.
%
Specifically, symbols representing the syntactic category and node
roles are treated as distinct vocabulary tokens, mapped to integers,
and used to retrieve a vector representation that is learned during
training.
%
The vectors are grouped into a tensor by placing the root node into
the first cell of the first row and left-aligning the descendants in
the subsequent rows.
%
The two tensors are concatenated along the embedding dimension.
%
This embed-and-group method is shown in on the left in Figure \ref{fig:spineembedding}.
%the root node is in first cell in the first row and the subsequent nodes are

@@

The use of topological indices allows for many recurrent tree networks to be
run in parallel on a GPU for efficiency.
%
GPU implementations must be formulated homogeneously so that 
the same operations are always applied to the entire data structure.
%
Normally, tree operations require flow control, making homogeneity
impossible.
%
However, using topological indices and a tree state eliminates the
need for flow control by creating locally linear, homogeneous
computations.
